Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2020-12-11 GWLDCI.tex
mostly working on paper 2

>>>>

There are many other instances of this basic methodology in combinatorics, but we'd like to point out one in particular that involves many objects closely related to those we use here, \cite{CGdyck}.\footnote{Thanks to the referee for the companion paper for pointing this out.}  In particular they, like us, look at a special case within the world of positroids and related objects which is enumerated by Catalan numbers.  For them these are positroids coming from unit interval graphs, while for us they are the equivalent exact subdiagrams.  Our objects are different, which can be seen by the fact that exact subdiagrams do not necessarily satisfy Lemma 4.1 of \cite{CGdyck}, but there are similarities in flavour with our arguments \hlfix{here and in our companion paper.}{Karen still needs to work on this}
